---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rspacer

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of rspacer is to wrap the [RSpace API](https://community.researchspace.com/public/apiDocs).

## Installation

You can install the development version of rspacer like so:

```{r, eval=F}
remotes::install_github("burgerga/rspacer")
```

## Usage

Add the environment files `RSPACE_API_URL` and `RSPACE_API_KEY` to your `.Renviron` file (you can do so using the `usethis::edit_r_environ()` command). Your `.Renviron` should contain the following lines:

```
RSPACE_API_URL="https://leiden.researchspace.com/api/v1"
RSPACE_API_KEY="<YOUR_API_KEY_HERE>"
```

The `RSPACE_API_URL` is typically the URL of your RSpace instance followed by `api/v1`.
To get your API key see the instructions in the **Authentication with an API key** section at <https://community.researchspace.com/public/apiDocs>.  
**Keep your API key private!**

After restarting R, you should now be able to run

```{r example}
library(rspacer)
api_status()
```

Now you can explore the functionality of `rspacer`.
